---
title: "R Notebook"
output: html_notebook
---


This is an attempt to keep track of my revolving and confused ideas about using color in plots.

I'm using this as a testing ground and someplace I can go to compare different color palettes for different plotting purposes. When I find color palettes I like that aren't implemented in R, I'll write ggplot `scale` functions and save them here.



Load in packages: 

```{r}
require(tidyverse)
require(viridis)
require(RColorBrewer)

```


## some colors schemes

### quantitative

```{r}

# red / orange / yellow
display.brewer.pal(name = "YlOrRd", n=10)

# yellow / green / blue
display.brewer.pal(name = "YlGnBu", n=10)

# viridis
ggthemr::colour_plot(viridis(10))

# magma
ggthemr::colour_plot(magma(10))


```


### qualitative

```{r}

# base colors
palette_base <- function(n, random_order = FALSE) {
  cols <- c("#ac4142",
            "#d28445",
            "#f4bf75",
            "#90a959",
            "#75b5aa",
            "#6a9fb5",
            "#aa759f",
            "#8f5536",
            "black")
  cols <- cols[c(1,6,5,2,7,4,8,3)]
  
  if (isTRUE(random_order))
    cols <- sample(cols)
  
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  
  cols[1:n]
  
}
scale_color_base<- function(...) discrete_scale("colour", "base", palette_base, ...)
scale_fill_base <- function(...) discrete_scale("fill", "base", palette_base, ...)


cols <- c("#ac4142",
          "#d28445",
          "#f4bf75",
          "#90a959",
          "#75b5aa",
          "#6a9fb5",
          "#aa759f",
          "#8f5536",
          "black")
cols <- cols[c(1,6,5,2,7,4,8,3)]

ggthemr::colour_plot(cols)




palette_charted <- function(n, random_order = FALSE) {
  cols2 <- c('#6DCC73', '#1D7775', '#4FCFD5', '#FCE651', '#FF7050', '#FFC050', '#999999')
  cols2 <- cols2[c(1,2,3,5,6,7,4)]
  
  if (isTRUE(random_order))
    cols2 <- sample(cols2)
  
  if (length(cols2) < n)
    cols2 <- rep(cols2, length.out = n)
  
  cols2[1:n]
  
}
scale_color_charted<- function(...) discrete_scale("colour", "charted", palette_charted, ...)
scale_fill_charted <- function(...) discrete_scale("fill", "charted", palette_charted, ...)



cols2 <- c('#6DCC73', '#1D7775', '#4FCFD5', '#FCE651', '#FF7050', '#FFC050', '#999999')
cols2 <- cols2[c(1,2,3,5,6,7,4)]
ggthemr::colour_plot(cols2)


wes_palette("Rushmore", 5)
palette_rushmore <- function(n, random_order = FALSE) {
  cols <- c("#E1BD6D", "#EABE94", "#0B775E", "#35274A", "#F2300F")
  cols <- cols[c(3,4,5,1,2)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_rushmore<- function(...) discrete_scale("colour", "rushmore", palette_rushmore, ...)
scale_fill_rushmore <- function(...) discrete_scale("fill", "rushmore", palette_rushmore, ...)


wes_palette("Zissou", 5)

palette_zissou <- function(n, random_order = FALSE) {
  cols <- c("#3B9AB2" ,"#78B7C5" ,"#EBCC2A" ,"#E1AF00", "#F21A00")
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_zis<- function(...) discrete_scale("colour", "zissou", palette_zissou, ...)
scale_fill_zis <- function(...) discrete_scale("fill", "zissou", palette_zissou, ...)



wes_palette("Darjeeling", 5)
palette_darjeeling <- function(n, random_order = FALSE) {
  cols <- c("#FF0000" ,"#00A08A" ,"#F2AD00" ,"#F98400", "#5BBCD6")
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_dar<- function(...) discrete_scale("colour", "darjeeling", palette_darjeeling, ...)
scale_fill_dar <- function(...) discrete_scale("fill", "darjeeling", palette_darjeeling, ...)





```




# colors in action

What I'm showing doesn't really matter--the goal is look at how the colors work together (or don't).

### quantitative

```{r fig.height=8, fig.width=8}
if (require("Lahman") && packageVersion("Lahman") >= "3.0.1") {
 
  batting <- tbl_df(Batting)
  
  a <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    scale_fill_base(guide = F) +
    ggtitle("base") +
    xlab("league") +
    ylab("average number of home runs")
  

  b<- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("charted") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_charted(guide= F)
  
  c<-batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("paired") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_brewer(palette = "Paired", guide = F)
  
  d<-batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("dark2") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_brewer(palette = "Dark2", guide = F)
  
  e <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("rushmore") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_rushmore(guide = F)
  
  f <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("dar") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_dar(guide = F)
  
  g <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("zis") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_zis(guide = F)
  
  
  cowplot::plot_grid(a,b,c,d,e,f,g, labels = c("a", "b", "c", "d", "e", "f","g"))
  
  
}

```

### qualitative

```{r fig.height=8, fig.width=8}


if (require("Lahman") && packageVersion("Lahman") >= "3.0.1") {
  set.seed(11)
  a <- batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_viridis() +
    ggtitle("viridis")
  
  set.seed(11)
  b <- batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_viridis(option = "magma") +
    ggtitle("magma")
  
  set.seed(11)
  c <- batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_distiller(palette = "YlOrRd") +
    ggtitle("YlOrRd")
    
  set.seed(11)
  d<-batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_distiller(palette = "YlGnBu") +
    ggtitle("YlGnBu")
  
  cowplot::plot_grid(a,b,c,d, labels = c("a", "b", "c", "d"))
   
}


```



