---
title: "color palettes"
output:
  html_document:
    toc: yes
  html_notebook:
    highlight: tango
    theme: readable
    toc: yes
---


This is an attempt to keep track of my revolving and confused ideas about using color in plots.

I'm using this as a testing ground and someplace I can go to compare different color palettes for different plotting purposes. When I find color palettes I like that aren't implemented in R, I'll write ggplot `scale` functions and save them here.



Load in packages: 

```{r}
require(tidyverse)
require(viridis)
require(RColorBrewer)
require(wesanderson)

```



## a good theme

`theme_mod` is is minimalist, modern theme that I like to use.


```{r}
theme_mod <- function(font_size = 14, font_family = "", line_size = .5, axes = F) {
  half_line <- 9
  small_rel <- 0.857
  small_size <- small_rel * font_size
  
  theme_grey(base_size = font_size, base_family = font_family) %+replace%
    theme(
      rect              = element_rect(fill = "transparent", colour = NA, color = NA, size = 0, linetype = 0),
      text              = element_text(family = font_family, face = "plain", colour = "black",
                                       size = font_size, hjust = 0.5, vjust = 0.5, angle = 0, lineheight = .9,
                                       margin = ggplot2::margin(), debug = FALSE),
      axis.text         = element_text(colour = "black", size = small_size),
      #axis.title        = element_text(face = "bold"),
      axis.text.x       = element_text(margin = ggplot2::margin(t = small_size / 4), vjust = 1),
      axis.text.y       = element_text(margin = ggplot2::margin(r = small_size / 4), hjust = 1),
      axis.title.x      = element_text(margin = ggplot2::margin(t = small_size / 2, b = small_size / 4)),
      axis.title.y      = element_text(angle = 90,margin = ggplot2::margin(r = small_size / 2, l = small_size / 4)),
      axis.ticks        = element_line(colour = "black", size = line_size),
      # axis.line = ifelse(axes == TRUE, element_line(colour = "black", size = line_size), element_blank()),
      axis.line = element_blank(),
      legend.key        = element_blank(),
      legend.spacing     = grid::unit(0.1, "cm"),
      legend.key.size   = grid::unit(1, "lines"),
      legend.text       = element_text(size = rel(small_rel)),
      #    legend.position   = c(-0.03, 1.05),
      # legend.justification = c("left", "right"),
      panel.background  = element_blank(),
      panel.border      = element_blank(),
      panel.grid.major  = element_blank(),
      panel.grid.minor  = element_blank(),
      strip.text        = element_text(size = rel(small_rel)),
      strip.background  = element_blank(),
      plot.background   = element_blank(),
      plot.title        = element_text(size = font_size*1.2, hjust = 0)
    )
}

# helper functions to change theme options
add_axes <- function(width = 0.6){theme(axis.line = element_line(colour = "black", size = width))}
remove_axes <- function(width = 0.6){theme(axis.line =element_blank())}
rotate_labels <- function(an = 45){theme(axis.text.x = element_text(angle = an, hjust=1))}





```



## some colors schemes

### quantitative

```{r}

# red / orange / yellow
display.brewer.pal(name = "YlOrRd", n=10)

# yellow / green / blue
display.brewer.pal(name = "YlGnBu", n=10)

# viridis
ggthemr::colour_plot(viridis(10))

# magma
ggthemr::colour_plot(magma(10))


# the following are taken from the seaborn plotting package for python
# greens
g <- c(0.8423298817793848, 0.8737404427964184, 0.7524954030731037,
         0.7161563289278935, 0.8232880086631527, 0.6542005475652726,
         0.5815252468131623, 0.7703468311289211, 0.5923205247665932,
         0.4576142801317438, 0.7057950454122253, 0.5634791991994519,
         0.35935359003014994, 0.6245622005326175, 0.554154071059354,
         0.2958858732022419, 0.532095403269888, 0.5458447574597934,
         0.25744332683867743, 0.42368146872794976, 0.5191691971789514,
         0.23607359470828057, 0.3125354171874312, 0.4605854787435648,
         0.21392162678343224, 0.20848424698401846, 0.3660805512579508,
         0.17250549177124488, 0.11951843162770594, 0.24320155229883056)
  
  greens <- c()
  for(i in seq(1, length(g), by = 3)){
    greens <- greens %>% c(rgb(g[i], g[1+i], g[2+i]))
  }
greens <- colorRampPalette(greens)

ggthemr::colour_plot(greens(10))

# create scale
scale_color_greens <- function (..., alpha = 1, begin = 0, end = 1, direction = 1) 
{
    if (direction == -1) {
        tmp <- begin
        begin <- end
        end <- tmp
    }
        scale_color_gradientn(colours = greens(256), ...)
}

# green / blue
b <- c(0.21697808798621682, 0.32733564601225013, 0.36941176807179171,
         0.23442778952760632, 0.45820839330261826, 0.54352941859002213,
         0.25140587751382315, 0.58554403931486831, 0.7129411866618138,
         0.32480841754308709, 0.68493145540648814, 0.7899474686267329,
         0.45066770474895151, 0.75099834881576832, 0.77038576275694604,
         0.58002308326608998, 0.81890043370863974, 0.75028067616855398)
  gb <- c()
  for(i in seq(1, length(b), by = 3)){
    gb <- gb %>% c(rgb(b[i], b[1+i], b[2+i]))
  }
gb <- colorRampPalette(gb)
ggthemr::colour_plot(gb(10))
# create scale
scale_color_gb <- function (..., alpha = 1, begin = 0, end = 1, direction = 1) 
{
    if (direction == -1) {
        tmp <- begin
        begin <- end
        end <- tmp
    }
        scale_color_gradientn(colours = gb(256), ...)
}

# purples
 p <- c(0.9537199587873054, 0.8839852653958624, 0.8572137883283991,
         0.903348395924016, 0.7454993373667652, 0.7391619965768441,
         0.8399541228445281, 0.6129917738874731, 0.6602115774420979,
         0.7513505093364804, 0.48945565575763195, 0.6018942098123031,
         0.6294330293285846, 0.3759488961295364, 0.5449881320264003,
         0.4874367518814018, 0.2815561055972257, 0.4759723295956624,
         0.326803151203735, 0.1959385410144846, 0.3750675408906117,
         0.1750865648952205, 0.11840023306916837, 0.24215989137836502)
  purples <- c()
  for(i in seq(1, length(p), by = 3)){
    purples <- purples %>% c(rgb(p[i], p[1+i], p[2+i]))
  }
  purples <- colorRampPalette(purples)
scale_color_purples <- function (..., alpha = 1, begin = 0, end = 1, direction = 1) 
{
    if (direction == -1) {
        tmp <- begin
        begin <- end
        end <- tmp
    }
        scale_color_gradientn(colours = purples(256), ...)
}
ggthemr::colour_plot(purples(10))

b <- c("#2A2A38", "#53395C", "#793E6E", "#A24169", "#C24456", "#E34C30", "#E47C61", "#E19F91", "#DAC2BE", "#D8DAD7", "#D2F8EF")
br <- colorRampPalette(b)
scale_color_brrr <- function (..., alpha = 1, begin = 0, end = 1, direction = 1) 
{
    if (direction == -1) {
        tmp <- begin
        begin <- end
        end <- tmp
    }
        scale_color_gradientn(colours = br(256), ...)
}
ggthemr::colour_plot(br(12))


```


### qualitative

```{r}

# base colors
palette_base <- function(n, random_order = FALSE) {
  cols <- c("#ac4142",
            "#d28445",
            "#f4bf75",
            "#90a959",
            "#75b5aa",
            "#6a9fb5",
            "#aa759f",
            "#8f5536",
            "black")
  cols <- cols[c(1,6,5,2,7,4,8,3)]
  
  if (isTRUE(random_order))
    cols <- sample(cols)
  
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  
  cols[1:n]
  
}
scale_color_base<- function(...) discrete_scale("colour", "base", palette_base, ...)
scale_fill_base <- function(...) discrete_scale("fill", "base", palette_base, ...)
ggthemr::colour_plot(palette_base(10))

palette_pen <- function(n, random_order = FALSE) {
  cols <- c("#ECC543", "#D85934", "#39454B", "#8EB9C3", "#7D7D7D", "black")
  cols <- cols[c(2,5,3,1,4,6)]

  if (isTRUE(random_order))
    cols <- sample(cols)
  
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  
  cols[1:n]
  
}
scale_color_pen<- function(...) discrete_scale("colour", "pen", palette_pen, ...)
scale_fill_pen <- function(...) discrete_scale("fill", "pen", palette_pen, ...)
ggthemr::colour_plot(palette_pen(10))




palette_charted <- function(n, random_order = FALSE) {
  cols2 <- c('#6DCC73', '#1D7775', '#4FCFD5', '#FCE651', '#FF7050', '#FFC050', '#999999')
  cols2 <- cols2[c(1,2,3,5,6,7,4)]
  
  if (isTRUE(random_order))
    cols2 <- sample(cols2)
  
  if (length(cols2) < n)
    cols2 <- rep(cols2, length.out = n)
  
  cols2[1:n]
  
}
scale_color_charted<- function(...) discrete_scale("colour", "charted", palette_charted, ...)
scale_fill_charted <- function(...) discrete_scale("fill", "charted", palette_charted, ...)



cols2 <- c('#6DCC73', '#1D7775', '#4FCFD5', '#FCE651', '#FF7050', '#FFC050', '#999999')
cols2 <- cols2[c(1,2,3,5,6,7,4)]
ggthemr::colour_plot(cols2)


wes_palette("Rushmore", 5)
palette_rushmore <- function(n, random_order = FALSE) {
  cols <- c("#E1BD6D", "#EABE94", "#0B775E", "#35274A", "#F2300F")
  cols <- cols[c(3,4,5,1,2)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_rushmore<- function(...) discrete_scale("colour", "rushmore", palette_rushmore, ...)
scale_fill_rushmore <- function(...) discrete_scale("fill", "rushmore", palette_rushmore, ...)

palette_classic <- function(n, random_order = FALSE) {
  cols <- c("#eaab00", "#004165","#236d01", "#eacb77", "#4686aa", "#65aa46" ,"#ea5d00", "#f29354")
  if (isTRUE(random_order))
    cols <- sample(cols)
  
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  
  cols[1:n]
  
}
scale_color_classic <- function(...) discrete_scale("colour", "classic", palette_classic, ...)
scale_fill_classic <- function(...) discrete_scale("fill", "classic", palette_classic, ...)
ggthemr::colour_plot(palette_classic(10) )

# base colors

wes_palette("Zissou", 5)

palette_zissou <- function(n, random_order = FALSE) {
  cols <- c("#3B9AB2" ,"#78B7C5" ,"#EBCC2A" ,"#E1AF00", "#F21A00")
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_zis<- function(...) discrete_scale("colour", "zissou", palette_zissou, ...)
scale_fill_zis <- function(...) discrete_scale("fill", "zissou", palette_zissou, ...)



wes_palette("Darjeeling", 5)
palette_darjeeling <- function(n, random_order = FALSE) {
  cols <- c("#FF0000" ,"#00A08A" ,"#F2AD00" ,"#F98400", "#5BBCD6")
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_dar<- function(...) discrete_scale("colour", "darjeeling", palette_darjeeling, ...)
scale_fill_dar <- function(...) discrete_scale("fill", "darjeeling", palette_darjeeling, ...)


palette_world <- function(n, random_order = FALSE) {
  cols <- c("#e39d25", "#d16050","#5cb3e7","#4676b1","#818b98","#4c4c4c", "black", "#323280")
  cols <- cols[c(3,4,1,2,5,6,7,8)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_world <- function(...) discrete_scale("colour", "world", palette_world, ...)
scale_fill_world <- function(...) discrete_scale("fill", "world", palette_world, ...)

ggthemr::colour_plot(palette_world(8))

palette_dark <- function(n, random_order = FALSE) {
  cols <- c("#3c2a21", "#a37c26","#a99b92","#1C4C68","#812e2c")
  cols <- cols[c(5,4,2,1,3)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_dark <- function(...) discrete_scale("colour", "dark", palette_dark, ...)
scale_fill_dark<- function(...) discrete_scale("fill", "dark", palette_dark, ...)

ggthemr::colour_plot(palette_dark(6))

palette_bright <- function(n, random_order = FALSE) {
  cols <- c("#eec589", "#573a3b","#55bbb1","#3c4a68","#6399b4", "#969696")
  cols <- cols[c(5,4,2,6,1,3)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_bright <- function(...) discrete_scale("colour", "bright", palette_bright, ...)
scale_fill_bright <- function(...) discrete_scale("fill", "bright", palette_bright, ...)

ggthemr::colour_plot(palette_bright(6))




palette_cb <- function(n, random_order = FALSE) {
  cols <- c("#44AA99",
            "#6699CC",
            "#332288",
            "#117733",
            "#88CCEE",
            "#661100",
            "#DDCC77",
            "#999933",
            "#CC6677",
            "#AA4466",
            "#882255",
            "#AA4499")
  cols <- cols[c(3,2,5,1,4,6:12)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  
  cols[1:n]
  
}
scale_color_cb<- function(...) discrete_scale("colour", "cb", palette_cb, ...)
scale_fill_cb <- function(...) discrete_scale("fill", "cb", palette_cb, ...)

ggthemr::colour_plot(palette_cb(12))

palette_powder <- function(n, random_order = FALSE) {
  cols <- c("#2c0703",
            "#890620",
            "#b6465f",
            "#da9f93",
            "#ebd4cb")
  if (isTRUE(random_order))
    cols <- sample(cols)
  
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  
  cols[1:n]
  
}
scale_color_powder <- function(...) discrete_scale("colour", "powder", palette_powder, ...)
scale_fill_powder <- function(...) discrete_scale("fill", "powder", palette_powder, ...)

ggthemr::colour_plot(palette_powder(5))


palette_ras <- function(n, random_order = FALSE) {
  cols <- c("#b33f62",
            "#0c0a3e",
            "#f9564f",
            "#7b1e7a",
            "#f3c677")
  cols <- cols[c(2,4,1,3,5)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  
  cols[1:n]
  
}
scale_color_ras <- function(...) discrete_scale("colour", "ras", palette_ras, ...)
scale_fill_ras <- function(...) discrete_scale("fill", "ras", palette_ras, ...)

ggthemr::colour_plot(palette_ras(5))

palette_blues <- function(n, random_order = FALSE) {
  # cols <- c("#8A0E38", "#1B95CF","#4D4768","#1B827F", "#C80E38", "#1E6496", "#64AA9D")
  cols <- c("#8A0E38", "#52B3D9","#674172","#16A085", "#CF000F", "#34495E", "#65C6BB")
  cols <- cols[c(6,7,4,1,5,3,2)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_blues <- function(...) discrete_scale("colour", "blues", palette_blues, ...)
scale_fill_blues <- function(...) discrete_scale("fill", "blues", palette_blues, ...)
ggthemr::colour_plot(palette_blues(7))


palette_brr <- function(n, random_order = FALSE) {
  # red, lighter purple, raspberry, orange, dark blue, orange,flesh, ice
  cols <- c("#D84541", "#783D6D", "#B44361", "#4E3759", "#D7D9D6", "#322E41", "#E46B4A", "#D4F2EB")
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_brr <- function(...) discrete_scale("colour", "brr", palette_brr, ...)
scale_fill_brr <- function(...) discrete_scale("fill", "brr", palette_brr, ...)
ggthemr::colour_plot(palette_brr(8))


palette_brew <- function(n, random_order = FALSE) {
  cols <- c("#4C9889", "#5E3F27", "#708CB0", "#2A534D", "#FFF55E", "#313752", "#FC6C64", "#FFAF4F", "#88211C")
  cols <- cols[c(1,2,3,4,6,8,9,7,5)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_brew <- function(...) discrete_scale("colour", "brew", palette_brew, ...)
scale_fill_brew <- function(...) discrete_scale("fill", "brew", palette_brew, ...)
ggthemr::colour_plot(palette_brew(9))


palette_puz <- function(n, random_order = FALSE) {
  cols <- c("#525164", "#A4C3B1", "#DB868C", "#4A6851", "#714738", "#FBDD93", "#C04839", "#D8924F","#EBA758")
  cols <- cols[c(1,4,2,5,9,6,3,7,8)]
  if (isTRUE(random_order))
    cols <- sample(cols)
  if (length(cols) < n)
    cols <- rep(cols, length.out = n)
  cols[1:n]
}
scale_color_puz <- function(...) discrete_scale("colour", "puz", palette_puz, ...)
scale_fill_puz <- function(...) discrete_scale("fill", "puz", palette_puz, ...)
ggthemr::colour_plot(palette_puz(9))
```




# colors in action

What I'm showing doesn't really matter--the goal is look at how the colors work together (or don't).

### quantitative

```{r fig.height=8, fig.width=8}


if (require("Lahman") && packageVersion("Lahman") >= "3.0.1") {
 
  batting <- tbl_df(Batting)
  
  a <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    scale_fill_ras(guide = F) +
    ggtitle("ras") +
    xlab("league") +
    ylab("average number of home runs")
  

  b<- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("world") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_world(guide = F)
  
  c<-batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("paired") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_brewer(palette = "Paired", guide = F)
  
  d<-batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("pen") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_pen(guide = F)
  
  e <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("brew") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_brew(guide = F)
  
  f <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("puz") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_puz(guide = F)
  
  g <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("blues") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_blues(guide = F)
  
  h <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("ptol") +
    xlab("league") +
    ylab("average number of home runs") +
    ggthemes::scale_fill_ptol(guide = F)
  
  j <- batting %>%
    group_by(lgID) %>%
    summarise(average_hr = mean(HR, na.rm = TRUE)) %>%
    ggplot(aes(lgID, average_hr)) +
    geom_bar(stat = "identity", aes(fill = lgID)) +
    theme_minimal() +
    ggtitle("classic") +
    xlab("league") +
    ylab("average number of home runs") +
    scale_fill_classic(guide = F)
  
  
  cowplot::plot_grid(a,b,c,d,e,f,g,h,j, labels = c("a", "b", "c", "d", "e", "f","g", "h", "j"))
  
  
}

```

### qualitative

```{r fig.height=8, fig.width=8}
# theme_set(theme_mod())

if (require("Lahman") && packageVersion("Lahman") >= "3.0.1") {
  set.seed(11)
  a <- batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_viridis() +
    ggtitle("viridis")
  
  set.seed(11)
  b <- batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_viridis(option = "magma") +
    ggtitle("magma")
  
  set.seed(11)
  c <- batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_distiller(palette = "YlOrRd") +
    ggtitle("YlOrRd")
    
  set.seed(11)
  d<-batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_distiller(palette = "YlGnBu") +
    ggtitle("YlGnBu")
  
  set.seed(11)
  e<-batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_greens() +
    ggtitle("greens")
  
  set.seed(11)
  f<-batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_gb() +
    ggtitle("gb")
  
  set.seed(11)
  g<-batting %>% 
    sample_n(1000) %>%
    ggplot(aes(SB, HR)) +
    geom_point(aes(color = H)) +
    theme_minimal() +
    scale_color_purples() +
    ggtitle("purples")
  
  cowplot::plot_grid(a,b,c,d,e,f,g, labels = c("a", "b", "c", "d","e","f","g"), ncol = 2)
   
}


```


